Dynamic Transition Analysis with TIMES

### 2019-05-09 doc/2019-05-report/2019-05-i2cner-report.tex
edited challenges, progress report
Former-commit-id: 3baa53917e6174d9d3674b37ef31e6861e5be301
Former-commit-id: 13afd68ce7589a0577d245316b37b72315cf5874

\item \textbf{October 2018 – April 2019:}

@@

@@

The project was significantly delayed due to the quality of the documentation and customer support provided by the VEDA developers. The primitive, black-box like nature of the software often produces inexplicable, illogical results and inhibits efficient debugging. Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule, by about three months. \\

In addition to having incomplete/inaccurate data for 2011, 2012 and 2016, \gls{EDMC} has been eliminating data related to electricity generation from individual fossil fuels and lumping power from coal, oil, and natural gas into a category called "thermal" in its databank. This complicates the process of estimating CO\textsubscript{2} emissions from these energy sources, since each fossil fuel has a different emission coefficient. Losing the primary data that we have been relying on has affected our pace and the reproducibility of our research significantly. The \gls{EDMC} databank figures in GWh, instead of in tons of coal or oil, have influenced our model's simplistic design, as discussed previously. Our efforts to find similar data have been unsuccessful. Switching to data in terms of the quantity of raw fossil fuels consumed instead of GWh of electricity produced may require a substantial revision of our model.

\section{Future Work}

>>>>

\item \textbf{October 2018 – January 2019:}

@@

\item \textbf{February 2019 – April 2019:}

\item \textbf{Gradual collection and replacement of \gls{LCoE} data with accurate cost structure:} The results presented at the \gls{I$^2$CNER} Annual \gls{EAD} workshop (see fig. \ref{some fig} ) were based entirely on \gls{LCoE} analysis, as \gls{LCoE} data and projections were readily available. However, it is more suitable to incorporate cost data in the recommended \gls{TIMES} format, that is with the investment/capital cost, fixed and variable operation and maintenance costs. This is due to the fact that when there is no investment cost associated with an energy source, the deplyment of a resource costs nothing, and hence the model may be retiring such capacity deployments before the end of their lifetime, which has been observed in a few bugs <ADD LINK/FIGURE>

@@

The project was significantly delayed due to the quality of the documentation and customer support provided by the VEDA developers. The primitive, black-box like nature of the software inhibits efficient debugging. Therefore, while data acquisition and organization proceeded at the originally suggested pace, the incorporation of this data into the model has been behind schedule. \\

The \gls{EDMC} is constantly being revised and updated, for both earlier (2010-2013) and later years(2016-). Hence, this data is not always consistent or complete, and often secondary sources must be used for verification.
\section{Future Work}
